<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-10 paper-supplementary.Rmd
supplementary plots done

```{r raw-data-50, out.width = "100%", fig.cap=" The raw half-hourly energy usage for $50$ sampled households is plotted along the y-axis versus time in a linear scale.  Each of these series is associated with a single customer. It looks like there is a lot of missing values and unequal length of time series along with asynchronous periods for which data is observed. No insightful behavioral pattern could be discerned from this view other than when the customer is not at home."}

@@

```{r missing-data, fig.cap="(ref:missing-data)"}
knitr::include_graphics("figs/missing-data-5050.png")
```

@@

# Interaction of granularities

>>>>

```{r raw-data-50, out.width = "100%", fig.cap=" The raw half-hourly energy usage for $50$ sampled households is plotted along the y-axis versus time in a linear scale.  Each of these series is associated with a single customer. It looks like there is a lot of missing values and unequal length of time series along with asynchronous periods for which data is observed. No insightful behavioral pattern could be discerned from this view other than when the customer is not at home.", fig.pos="h"}

@@

```{r missing-data, fig.cap="(ref:missing-data)", fig.pos="h"}
knitr::include_graphics("figs/missing-data-5050.png")
```

@@

<!-- # Interaction of granularities -->
